---
title: "Lab13"
author: "Jason Chen"
date: "2024-12-02"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Task 1
```{r}
  getwd()
```

# Task 2

## var.test()
```{r}
set.seed(13); x=rnorm(40,mean=15,sd=5)# 1
set.seed(20); y=rnorm(35,mean=10,sd=4)# 2

var.test(x,y)# 3
```
The population variances could be equal.

The p-value = 0.7119, which is greater than 0.05. So we fail to reject the null hypothesis.

## Hypothesis
$$
  H_0 = \mu_x \leq \mu_y \\
  H_1 = \mu_x > \mu_y
$$

## Test
```{r}
  t.test(x,y, var.equal = TRUE, alternative = "greater")
```

The NULL hypothesis is rejected.

The 95% confidence interval is (3.6322, Inf).

The confidence interval shows that the difference in the mean is at least 3.6322 with 95% confidence.

## Adjusting Mean
```{r}
  set.seed(20); y=rnorm(35,mean=14,sd=4)
  t.test(x,y,alternative = "greater")
```

The p-value = 0.09581, which is greater than 0.05, so we fail to reject the NULL hypothesis.

The confidence interval is (-0.3606, Inf). This shows that difference in the mean of the two samples is at least -0.3606 with 95% confidence.

# Task 3
```{r}
set.seed(50); x=rnorm(30,mean=50, sd=10)
set.seed(40); y=rnorm(40,mean=55, sd=20)

var.test(x,y) #1
var.test(y,x) #2
```

## P-value



```{r}
var.test(x,y,alt="less")#3
var.test(y,x,alt="greater")#4

```






